[dcpo_demsupport]

### 2020-09-03 paper/dcpo_demsupport.Rmd
apsr with trimmed data

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

@@

df_plot <- df_result_dcpoMean[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpo[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

@@

df_plot <- df_result_dcpoMean[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpo[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

@@

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "APSRctlv.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

@@

mods[[2]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

@@

estimate_dcpo[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
      model = "pooling",
      data = aDataset
    )
}

@@

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)",
      "Corruption\n (Difference)",
      "Corruption\n (t−1)"
      ),time = 2)
  )

>>>>

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= firstyear) # using trimmed data as Claassen

@@

df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAJPS[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

@@

df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAJPS[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

@@

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

@@

mods[[2]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

@@

estimate_dcpo[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
      model = "pooling",
      data = aDataset
    )
}

@@

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic\n Mood\n (t-1)",
        "Democratic\n Mood\n (t-2)",
      "Liberal\n Democracy\n (Difference)",
      "Liberal\n Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)",
      "Corruption\n (Difference)",
      "Corruption\n (t−1)"
      ),time = 2)
  )
